Image reconstruction of stellar objects with Intensity Interferometry using Generative Adversarial Networks

### 2025-02-02 Phase_II/draft/GAN.tex
Changes by Sarangi

\section{Generative Adversarial Networks}
Generative Adversarial Networks (GANs) were invented by Ian Goodfellow in 2014. The concept is rather simple, as it consists of two competing networks. The first network is called a generator and creates new images based on an input image. Here, for consistency, the images generated by the generator will be denoted as generated images. The second network is the discriminator, which tries to distinguish between the generated image and the real image (ground truth) \citep{goodfellow2014generative}.
As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images. It is nothing more than a two-player min-max game, a famous problem in game theory. GAN was initially proposed in the formulation form as:
\begin{equation}
	\centering
	\begin{aligned}
		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
	\end{aligned}
	\label{eq:Basic_GAN}
\end{equation}
here, $V(D, G)$ is the value function of the min-max game.

The goal is now to learn the distribution of the generator $p_g$ over the data $x$. We have input noise variables $p_z(z)$, as well as the two perceptrons $G(z; \theta_g)$ and $D(x; \theta_d)$ with parameters $\theta_i$. $G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \citep{goodfellow2014generative}. The problem can be reformulated as: 

@@

where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator and is expressed as

@@

It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$. Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$. A more detailed discussion of the problem, including proofs, can be found in \citep{goodfellow2014generative}.

@@

GAN can be extended to a conditional model \citep{mirza2014conditional}. In this case, both generator and discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) can be expressed as:

@@

Furthermore, \cite{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the generator tries to be close to the ground truth. Hence, the function that is minimized as:
\begin{equation}
	\centering
	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G)
	\label{eq:total_gen_loss}
\end{equation}
where $\lambda$ = 100 and $L_1(G)$ is given as
\begin{equation}
	\centering
	L_1(G) = \mathbb{E}_{x,y,z} \left[ ||{y - G(x,z)}||_1 \right]
	\label{eq:l1_loss}
\end{equation}

@@

\subsection{Generator}
The used generator in this paper is a common U-Net convolutional network \citep{ronneberger2015u}. It consists of a contracting part, reducing the image size, and an expansive part, where the image is enlarged. The contracting part consists of repeated application of alternating convolutional layers and rectified linear unit (ReLU) layers. The expansion consists of repeated convolution, batch normalization, and ReLU layers. The first contracting step also includes a dropout layer \citep{isola2017image}.

\subsection{Discriminator}
The discriminator that has been taken here, named PatchGAN, does not work globally but rather classifies single patches as real or fake. The overall result is then estimated based on the average. The model architecture is as follows: zero padding, convolution, batch-norm, ReLu, zero-padding, and convolution \citep{isola2017image}.

>>>>

\section{Generative Adversarial Networks}
Generative Adversarial Networks (GANs) were invented by Ian Goodfellow in 2014. The concept is rather simple, as it consists of two competing networks. The first network is called a generator and creates new images based on an input image. Here, for consistency, the images generated by the generator will be denoted as generated images. The second network is the discriminator, which tries to distinguish between the generated image and the real image (ground truth) \cite{goodfellow2014generative}.
As a consequence of training both networks alternately, the generated images eventually become indistinguishable from the real images. It is nothing more than a two-player min-max game, a famous problem in game theory. GAN was initially proposed in the formulation form as:
\begin{equation}
	\centering
	\begin{aligned}
		\min_{G} \max_{D} V(D, G) &= \mathbb{E}_{x \sim p_{data}(x)} \left[ \log D(x) \right] \\
		&+ \mathbb{E}_{z \sim p_{z}(z)} \left[ \log \left( 1-D(G(z)) \right) \right]
	\end{aligned}
	\label{eq:Basic_GAN}
\end{equation}
here, $V(D, G)$ is the value function of the min-max game.

The goal is now to learn the distribution of the generator $p_g$ over the data $x$. We have input noise variables $p_z(z)$, as well as the two perceptrons $G(z; \theta_g)$ and $D(x; \theta_d)$ with parameters $\theta_i$. $G$ represents a differential function that maps from $z$ to the data space $x$, while $D(x)$ represents the probability that $x$ is from the real data \cite{goodfellow2014generative}. The problem can be reformulated as: 

@@

where $D^{*}_{G}$ denotes the optimum of the discriminator for a given fixed generator, shown in equation (\ref{eq:Disc_optimum}). It can now be shown that the global optimum of equation (\ref{eq:GAN_reformulated}) is reached if and only if $p_g = p_{data}$. Furthermore, if both $G$ and $D$ are allowed to reach their optima, $p_g$ converges to $p_{data}$. A more detailed discussion of the problem, including proofs, can be found in \cite{goodfellow2014generative}. 

@@

@@

GANs can be extended to a conditional model \cite{mirza2014conditional}. In this case, both generator and discriminator receive extra information $y$, such that the value function of the conditional GAN (cGAN) can be expressed as:

@@

Furthermore, \cite{isola2017image} observed that combining the cGAN given in equation \ref{eq:conditional_GAN} with the traditional L1-loss improves results, as the generator tries to be close to the ground truth. Hence, the function that is minimized as:
\begin{equation}
	\centering
	L_{tot} = \arg \min_{G} \max_{D} V(D, G) + \lambda \cdot L_1(G)
	\label{eq:total_gen_loss}
\end{equation}
where $\lambda$ = 100 and $L_1(g)$ is given by equation (\ref{eq:l1_loss})
\begin{equation}
	\centering
	L_1(g) = \mathbb{E}_{x,y,z} \left[ \norm{y - G(x,z)}_1 \right]
	\label{eq:l1_loss}
\end{equation}

@@

\subsection{Generator}
The used generator in this paper is a common U-Net convolutional network, described in \cite{ronneberger2015u}. It consists of a contracting part, reducing the image size, and an expansive part, where the image is enlarged. The contracting part consists of repeated application of alternating convolutional layers and rectified linear unit (ReLU) layers. The expansion consists of repeated convolution, batch normalization, and ReLU layers. The first contracting step also includes a dropout layer \cite{isola2017image}

\subsection{Discriminator}
The discriminator that has been taken here, named PatchGAN, does not work globally but rather classifies single patches as real or fake. The overall result is then estimated based on the average. The model architecture is as follows: zero padding, convolution, batch-norm, ReLu, zero-padding, and convolution \cite{isola2017image}.
